Converting LaTeX R Journal Articles into Rmarkdown using texor and rebib

### 2023-07-26 texor.Rmd
Lua filters - but still needs more work

LaTeX is very descriptive language, that allows authors substantial freedom for customization. Markdown [@markdown], on which R Markdown is based, is more restrictive and was born to make it easier to create web pages without the distraction of a gazillion HTML tags. The purpose of Markdown is that it allows the author to focus on writing, without format cluttering the text.

@@

This was one of the earliest and most basic Lua filters, and it was part of the \CRANpkg{texor} package:

@@

Above filter reads the abstract syntax tree and filters out all the Div elements. Then it looks for the class "thebibliography." It turns out that this Div element  contains the LaTeX bibliographic records, which usually appear at the very end 
of papers. We don't need this portion in the article with the "RJ-web-article" layout,  given its inclusion as meta-data in the footer.

>>>>

LaTeX is very descriptive language, that allows authors substantial freedom for customization. Markdown [@markdown], on which R Markdown is based, is more restrictive and was born to make it easier to create web pages without the distraction of a gazillion HTML tags. The beauty of Markdown is that it allows the author to focus on writing, without format cluttering the text. The drawback is that it is simple typesetting, optimized for web delivery.

@@

Lua [@lua] is a programming language, that is light-weight, fast, ideal for procedural operations.  It is embedded in many other applications to allow custom scripting for extensibility. Pandoc allows users to provide custom lua filters to produce custom output formats. The \CRANpkg{texor} package handles post-processing of the R Markdown document into the special format for the R Journal using a suite of Lua filters.

Here is an example of a Lua filter in \CRANpkg{texor}:

@@

This filter reads the abstract syntax tree and filters out all the Div elements. Then it looks for the class "thebibliography." It turns out that this Div element  contains the LaTeX bibliographic records, which usually appear at the very end of papers. We don't need this portion in the article with the "RJ-web-article" layout,  given its inclusion as meta-data in the footer.

### 2023-07-26 texor.tex
Lua filters - but still needs more work

LaTeX is very descriptive language, that allows authors substantial freedom for customization. Markdown (Gruber 2002), on which R Markdown is based, is more restrictive and was born to make it easier to create web pages without the distraction of a gazillion HTML tags. The purpose of Markdown is that it allows the author to focus on writing, without format cluttering the text.

@@

This was one of the earliest and most basic Lua filters, and it was part of the \CRANpkg{texor} package:

@@

Above filter reads the abstract syntax tree and filters out all the Div elements. Then it looks for the class ``thebibliography.'' It turns out that this Div element contains the LaTeX bibliographic records, which usually appear at the very end
of papers. We don't need this portion in the article with the ``RJ-web-article'' layout, given its inclusion as meta-data in the footer.

@@

>>>>

LaTeX is very descriptive language, that allows authors substantial freedom for customization. Markdown (Gruber 2002), on which R Markdown is based, is more restrictive and was born to make it easier to create web pages without the distraction of a gazillion HTML tags. The beauty of Markdown is that it allows the author to focus on writing, without format cluttering the text. The drawback is that it is simple typesetting, optimized for web delivery.

@@

Lua (Ierusalimschy, Figueiredo, and Filho 1996) is a programming language, that is light-weight, fast, ideal for procedural operations. It is embedded in many other applications to allow custom scripting for extensibility. Pandoc allows users to provide custom lua filters to produce custom output formats. The \CRANpkg{texor} package handles post-processing of the R Markdown document into the special format for the R Journal using a suite of Lua filters.

Here is an example of a Lua filter in \CRANpkg{texor}:

@@

This filter reads the abstract syntax tree and filters out all the Div elements. Then it looks for the class ``thebibliography.'' It turns out that this Div element contains the LaTeX bibliographic records, which usually appear at the very end of papers. We don't need this portion in the article with the ``RJ-web-article'' layout, given its inclusion as meta-data in the footer.

@@

\leavevmode\vadjust pre{\hypertarget{ref-lua}{}}%
Ierusalimschy, Roberto, Luiz Henrique de Figueiredo, and Waldemar Celes Filho. 1996. {``Lua---an Extensible Extension Language.''} \emph{Software: Practice and Experience} 26 (6): 635--52.
